\documentclass{article}

\title{\large What I Want to Be When I Grow Up: The Next Three Years}
\author{Matthias Felleisen}
\date{\small 25 March 2015}

\usepackage{hyperref}

\begin{document}

\maketitle 
\thispagestyle{empty}

\begin{quote}
\footnotesize {\it Hacker News, today\/}: I can't praise HtDP enough. What
 [it] did was sufficient to fundamentally change me as a programmer. \ldots
 know that I am sincerely grateful for all of your work. Without the
 software and materials that you\ldots labored to create -- and \ldots
 provide freely -- I might not be a professional programmer today.
\end{quote}

\paragraph{Thesis} My teaching often inspires research projects, and my
 research projects tend to influence my teaching. This thesis guides my
 approach to academia. 

\paragraph{Research} For the past 20 years, I have pursued the vision of a
 programming language that narrows the gap between problem solving and
 programming.\marginpar{\tiny\raggedright\href{http://www.ccs.neu.edu/home/matthias/Tmp/manifesto/index.html}{\underline{The
 Racket Manifesto}}. In {\it SNAPL\/} 2015.}  This pursuit includes
 research on systematic program design (as problem solving); on programming
 languages that facilitate the creation of problem-specific languages; and
 on a full-spectrum language so that programmers can move from prototype to
 ``hardened'' product in one comprehensive framework.

For the next three years, I plan on focusing on this ``hardening'' aspect
 of the agenda, also known as the ``soft typing'' project. I have recruited
 several PhD students who are interested in this agenda, and I have
 submitted two NSF proposals (one large, one medium) and an ONR white paper
 to finance it all.  While I am the sole author, I have several co-PIs,
 including Jan V., who coined the phrase ``hardening'' for this project,
 and Olin S. (plus six others).

\paragraph{Teaching} I am the intellectual architect of the core
 programming undergraduate curriculum (Fundamentals~I--IV plus Logic). I
 intend to help maintain and improve it. What is missing, is a course
 focused on program design in a concurrent-distributed setting, which is
 why I am trying to recruit Heather M.

I intend to finish {\it How to Design Programs} (2) this year; it's a 10-year
 project. 

The new {\em Rust\/} course is an experiment in exposing students to
 cutting-edge research developments from industry with potential for future
 collaborations. 

At the PhD level, I wish to collaborate with Amal A.\ to improve iPPL. If
 possible, I would also like to teach ``History'' again; it has been five
 years.

\paragraph{Service} I serve where I see a need: integrate new faculty via
 research and teaching collaborations, mentor all PhD students in our lab,
 checking on our instructors (retaining the good ones, recruiting new ones)
 spot problems with courses, find faculty that expand our critical teaching
 mission, and make myself available where needed (but not chairing anything).

\end{document}
