\documentclass[11pt]{article}

%% hello

\input{preamble}

\begin{document}

\thispagestyle{empty}

\def\dollars#1{\relax}

\def\Litem#1{\par\begingroup\clubpenalty=10000% 
           \def\par{\endgraf\endgroup}
	   \noindent\hangindent=4cm\hangafter=0
	   \hbox to0pt{\hskip-3cm#1\hfill}}
\def\litem#1{\par\begingroup\clubpenalty=10000%
           \def\par{\endgraf\endgroup}
	   \noindent\hangindent=2cm\hangafter=0
	   \hbox to0pt{\hskip-2cm#1\hfill}}
\def\nl{\hfill\break}

\centerline{\sc Matthias Felleisen}

\bigskip

\centerline{College of Computer and Information Science}
\centerline{Northeastern University}
\centerline{Boston, MA 02115}
% \centerline{(617)373-2085}

\bigskip 

%% -----------------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Education}

\litem{1987}Indiana University, Bloomington, Indiana, Ph.D. in Computer Science. 
\litem{1983}Technische Universit\"at Karlsruhe, Germany, Dipl. WiIng.
\litem{1981}The University of Arizona, Tucson, Arizona, M.S. in Computer Science.

\bigskip

%% -----------------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Academic Appointments}
\litem{2001-- $\ldots$}Trustee Professor, Northeastern University, Boston, MA.
\litem{1993--2001}Professor, Rice University, Houston, Texas.
\litem{Sum.\ 91, 97}Visiting Professor, \'Ecole Normale Superi\'eure Paris, France.
\litem{1993--1994}Visiting Professor, Carnegie Mellon University, Pittsburgh.
\litem{1992--1993}Associate Professor, Rice University, Houston, Texas.
\litem{1987--1992}Assistant Professor, Rice University, Houston, Texas.

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Research Interests} My research interests cover all aspects
of program design and programming language design. In terms of teaching, I
am interested in all courses in the computer science core curriculum,
covering program design for applications, components, and systems plus the
underlying logics.\footnote{The study of logics relates to programming like
analysis relates to engineering.}

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent 
\noindent{\sc Major Products} I am the
founder of PLT (1993), a distributed research group that jointly produces
the {\bf Racket} programming language, the {\bf DrRacket} IDE, and plug-in
tools (the Stepper, the Macro Debugger, the PLT Web Server, 
etc).  The tools are used in educational outreach projects as well as
industrial projects.

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent{\sc Books}

\litem{2015}{\it How to Design Programs\/} (Second Edition). MIT Press. 
(With same authors as the first edition)

\litem{2013}{\it Realm of Racket: For Freshmen, by Freshmen}. NoStarch Press.
(With Forrest Bryce, Rose DeMaio, Spencer Florence, Mimi Lin, Scott
Lindemann, Nicole Nussbaum, Eric Peterson, Ryan Plessner, David Van Horn,
Conrad Barksi)

\litem{2010}{\it Semantics Engineering with PLT Redex}. MIT Press. 
Korean: 2012.
(With Findler and Flatt)

\litem{2001}{\it How to Design Programs\/}. MIT Press. 
Korean: 2012.
Spanish: 2008.
Chinese: 2003. 
Polish: 2002.
(With Robert Findler, Matthew Flatt, Shriram Krishnamurthi)

\litem{1998}{\it A Little Java, A Few Patterns\/}, MIT Press. Japanese
translation: 1998. (With Friedman) 

\litem{1998}{\it The Little MLer\/}. MIT Press. (With Friedman)

\litem{1996}{\it The Seasoned Schemer}. MIT Press. (With Friedman)

\litem{1996}{\it The Little Schemer\/}  (Fourth Edition).  MIT Press. 
Third: 1989, MacMillan. 
Second: 1985, Science Research Associates.
Japanese: 1990.
French: 1991.
(With Daniel P. Friedman)

%% -----------------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Publications in Journals and Highly Selective Conferences} 

\noindent I have published over 100 papers in journals and highly selective
conferences.\footnote{While conference publications are merely reviewed
rather than refereed, they go through a rigorous selection process and are
often larger and more comprehensive than journal papers in computer science
and neighboring disciplines.} Google Scholar attributes approximately
10,000 citations to my publications, which places me in the top-10 cited
scholars of my area.\\

\litem{1998}{Flatt, M., S. Krishnamurthi, M. Felleisen}.
 A programmer's reduction semantics for classes and mixins. 
 J. Alves-Foss (Ed.), {\it Formal Methods for Java\/}.
 {\bf LNCS 1523}. 1998, 241--270.

\litem{1997}Ariola, Z. M. Felleisen, 
 The Call-By-Need Lambda Calculus.
 {\it J. Funct. Progr. \bf7\/}, 265--301.

\litem{1994}{Wright, A. M. Felleisen}.
 A syntactic approach to type soundness.  {\it Info. \& Compu}.~38--94.

\litem{1993}{Flanagan, C., A. Sabry, B.F. Duba, M. Felleisen}.  The
essence of compiling with continuations.  In {\it Conference on
Programming Language Design and Implementation}, 1993, 237--247.

\litem{1992}{Felleisen, M. R. Hieb}.
The revised report on the syntactic theories for control and state.
{\it Theoretical Computer Science \bf102},~235--272.

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Active Grants} 

\noindent I have obtained around 35 grants from the AFOSR, ARO, Darpa,
DoED, NSF, and the Texas Advanced Technology Program plus gifts from Cisco,
Cord.org, Exxon, and Microsoft. \\

\litem{2014--2017}Compiler Coaching. With Tobin-Hochstadt (Indiana). NSF. 
\dollars{500,000}
\litem{2014--2017}Run Your Research with Redex. With Flatt (Utah) and Findler (NWU). NSF. 
\dollars{800,000}
\litem{2011--2014}Semantics Engineering. With Krishnamurthi~(Brown) and Findler~(NWU). NSF. 
\dollars{1,299,000}
\litem{2010--2015}Gnosys. With O. Shivers \& M. Wand. DARPA.
\dollars{2,400,000}
\litem{2009--2014}A Hot-House for Programming Languages. NSF. 
\dollars{684,000}

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Major Awards}

\noindent I consider the following six awards my most significant ones.  

\litem{2012}ACM SIGPLAN Most Influential ICFP Paper Award 
\litem{2012}ACM SIGPLAN Lifetime Achievement Award 
\litem{2011}ACM SIGCSE Outstanding Educator Award 
\litem{2009}ACM Karl V. Karlstrom Outstanding Educator Award 
\litem{2007}ACM Fellow 
\litem{1980--1981}Fulbright Fellowship

\bigskip

% -------------------------------------------------------------------
\noindent\hrulefill\\\noindent
\noindent {\sc Major Keynotes} 

\noindent I have given over 20 keynotes at most major research conferences in my area.

\litem{2011}{\it How to Design Programs\/}. SIGCSE. Dallas, Texas.

\litem{2010}{\it The TeachScheme! Project\/}. ICFP. Baltimore, Maryland.

\litem{2004}{\it Functional Classes, Functional Objects\/}. ECOOP. Oslo, Norway.

\litem{2002}{\it From POPL to the Classroom and Back\/}. POPL. Portland, Oregon.

\litem{2000}{\it Static Analysis from one Consumer's Perspective.\/}
SAS. Santa Barbara, California.  

\litem{2011}% I was the first speaker to present functional programming languages on Goldman Sachs TV.\\
{\it Functional Programming is Easy, and Good for You\/}

\end{document}
