\documentclass[11pt]{article}

\usepackage{fullpage}

\begin{document}

\section*{Matthias Felleisen}

\paragraph{Research Interests} I am interested in all aspects of
 programming languages and program design. I am the founder of PLT, a
 network of PL researchers who share a common code base (PLT Scheme). My
 research usually exploits this code base. In addition, all of my research
 involves teaching interests and vice versa.

\paragraph{Three most descriptive recent papers} 
\begin{enumerate}
\item Tobin-Hochstadt, Felleisen. ``The design and
implementation of Typed Scheme.'' {\it POPL\/} 2008. 

\item Eastlund, Felleisen. ``Making induction manifest in
Modular ACL2.'' {\it PPDP\/} 2009. 

\item Felleisen, Findler, Flatt, Krishnamurthi. ``A Functional I/O
System.'' {\it ICFP\/} 2009 
\end{enumerate}
 See {\tt http://www.ccs.neu.edu/home/matthias/papers.html}

\paragraph{Current PhD students and topics} 
\begin{enumerate}
\item Sam Tobin-Hochstadt. Enriching scripts with types. 
Will finish by end of 2009. Post-doc at Northeastern, financed by Mozilla. 

\item Ryan Culpepper. Taming, debugging, and fortifying Macros. 
Will finish by end of 2009. Most likely post-doc at Utah. 

\item Carl Eastlund. Equipping the ACL2 theorem prover with modern
linguistic structures. 

\item Stevie Strickland. Contracts and types for first-class classes. 

\item Christos Dimoulas. On the nature of contracts in higher-order,
imperative languages. (Joint with Riccardo Pucella)
\end{enumerate}
 Stephen Chang is exploring various topics concerning lazy languages with
 me to determine whether we are a suitable match. I also work with Eli
 Barzilay, a research scientist who helps maintain the PLT code base. 

\paragraph{Former PhD students and current employment} 
Richard Cobbe (2008), researcher, MathWorks (Boston (MA)); 
Philippe Meunier (2006), lecturer (assistant professor), IIIT Bangok (Thailand); 
John Clements (2005), assistant professor, CalPoly; 
Paul Graunke (2003), researcher, Galois Inc. (Portland); 
Robert Findler (2001), assistant professor, Northwestern; 
Shriram Krishnamurthi (2000), associate professor, Brown; 
Matthew Flatt (1999), associate professor, University of Utah; 
Cormac Flanagan (1997), professor, UC Santa Cruz; 
Amr Sabry (1994), professor, Indiana University; 
Andrew Wright (1994), CTO, N-Dimension (Richmond Hill (CN));
Dorai Sitaram (1994), researcher, Verizon (GTE Lab, Boston); 
Rebecca Parsons (1992), consultant, ThoughtWorks (London (UK))

\thispagestyle{empty}

\end{document}
