\documentstyle[12pt,abstract]{article}
\begin{document}
\subsection*{Presentations}

\begin{enumerate}
\item ``Types, Soft Types, and More Types.'' Dagstuhl Seminar on ``Latently
Typed Languages.'' May 2006. 

\item ``Teaching with Latentely Typed Languages in the First Year.''
Dagstuhl Seminar on ``Latently Typed Languages.'' May 2006. 

\item ``Interface-Oriented Programming.'' Max Planck Institute for Software
Systems. Kaiserslautern. April 2006. 

\item ``The First Year: Programming and Computer Science'' Universit{\"a}t
Darmstadt. March 2006. 

\item ``Interface-Oriented Programming.'' Universit{\"a}t Darmstadt. March
2006. 

\item ``How to Design Class Hierarchies'' Keynote Address. {\it Workshop
 Functional and Declarative Programming in Education\/}. September 2005.

\item ``Functional Objects, Functional Classes.'' Keynote Address. European
 Conference on Object-Oriented Programming Languages. Oslo, Norway, 2004

\item ``How many continuations can dance on the head of a pin.'' Invited
 talk. International Lisp Conference, NYC, 2003.

\item ``Why Teaching Novices Poses Interesting Challenges.'' Harvard U. 
March 2003. 

\item `` Programming Interactive Scripts for the Web.'' LU M\"unchen,
Bavaria, Germany. February 2003.  

\item ``The Human-Language Interface.''
UNAM. Mexico City, Mexico. January 2003. 

\item ``Next Generation Software Systems and Programming Languages.'' 
Northeast Programming Languages Workshop. Keynote talk. IBM Watson, May
2002.  
\item ``Next Generation Software Systems and Programming Languages.'' 
Simposium Internacional de Sistemas Computacionales, Mexico
City, Mexico. Keynote Address. April 2002.
\item ``Why Teaching Novices Poses Interesting Challenges.'' Microsoft
Research, Redmont, March 2002. 
\item ``From POPL to the Classroom and Back.'' POPL 2002. Portland,
Oregon. Invited talk. January 2002. 

\item ``Why are they still teaching Scheme when Haskell is so much
better?'' At IFIP Working Group 2.3, 2001, Dartmouth. 
\item ``Patterns in the Classroom'', NDIST Workshop, St John, December
2001. Joint keynote address with Daniel Jackson (MIT). 
\item ``From Patterns to Programming Languages'', NDIST Workshop, St John,
December2001.  
\item ``Programming Interactive Scripts for the Web.'' Yale University,
November 2001.  
\item ``Programming Interactive Scripts for the Web.'' NU ACM Chapter, October
2001.  
\item ``Programming Interactive Scripts for the Web.'' University of Texas at
Dallas, May 2001.  

\item{}``Behavioral Contracts for Java.'' Houston Java User Group. September 2000. 
\item{}``TeachScheme!: How to Train the Best Possible OO Programmers.''
Universit{\'e} de Montr\'eal, September 2000. 
\item{}``Behavioral Contracts for Java.'' INRIA, Sophia-Antipolis, July 2000. 
\item{}``TeachScheme!: How to Train the Best Possible OO Programmers.''
Universit{\'e} Nice (ESSI), July 2000. 
\item{}``Program Analyses: A Consumer's Perspective '' Static Analysis
Symposium, Invited Talk. UC Santa Barbara, June 2000. 
\item{}``Behavioral Contracts for Java.'' Universit{\"a}t Frankfurt, April 2000. 

\item{}``The Meaning of Contracts.'' University of Chicago, December 1999. 
\item{}``TeachScheme!: Programming For All (Students)''
 University of Chicago, December 1999. 
\item{}``The Meaning of Contracts.''
 {\em Inaugural Workshop of Preuves, Programmes, et Systemes\/}, Paris, 
 France. October, 1999. 
\item{}``Building Extensible Software''
 National Instruments, Austin, TX, June 1999. 
\item{}``Does Functional Programming Matter in an Object-Oriented World?''
 Indiana University, Bloomington, Indiana, March 1999.
\item{}``Safety as a Software Metric''
 {\em 12th Conference on Software Engineering
 Education and Training \rm(CSEE\&T'99)}; Invited Position Paper,
 March 1999.

\item{}``Building Extensible Software''
Horizon Day, Indiana University, Bloomington, Indiana, 1998.

\item{}``A Design-Based Introductory Course for Computer Science''
 FIE NSF Showcase Project, Invited Talk, Pittsburgh, November 1997.
\item{}``DrScheme: A pedagogic programming environment''
 PLILP, Southampton, September, 1997.
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' Carnegie Mellon University, Pittsburgh, April 1997.
\item{}``The Rice University Educational Infratstructure Project.''
Carnegie Mellon University, Pittsburgh, April 1997.
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' University of Oregon, Eugene, April 1997.
\item{}``The Rice University Educational Infratstructure Project.''
University of Oregon, Eugene, April 1997.
\item{}``Teaching the Principles of Computing.'' Texas Computer Educator
Association Conference. Houston, September 1996.
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' CUNY Graduate Center, New York City, August 1996.
\item{}``Teaching Design Principles in Introductory Courses.''
{\it Workshop on TEACHING FORMAL METHODS\/}. Stevens Institute of
Technology, Hoboken, NJ. July 1996.  
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' Ecole Normale Superiere, Paris, July 1996.
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' INRIA, Paris, July 1996.
\item{}``Towards Modular Soft Typing'',  Ecole Normale Superiere, 
Paris, June 1996.
\item{}``Constructing Reliable Software with Smart Programming
Environments.'' University of Houston, March 1996.
\item{}``The Rice Educational Infrastructure Project.'' 
Invited talk at: {\it Scheme Anniversay Workshop\/} (at POPL),
St. Petersburg, January 1996.
\item{}``Two Models of Memory Allocation and Their Uses.'' The
Newton Institute, Cambridge, England. November 1995. 
\item{}``Teaching Design Principles in Introductory Courses.''
{\it Workshop on EXPLORING FORMAL METHODS IN THE COMPUTER SCIENCE
CURRICULUM\/}. CUNY, Graduate Center, New York  City, September 1995. 
\item{}``Calculating with Scheme.''
Universit\'{e} Li{\`e}ge, Belgium. May 1994. 
\item{}``Extensible Denotational Language Specifications.''
Invited talk at: {\it Theoretical Aspects of Computer Software\/},
Sendai, Japan.  April 1994. 
\item{}``Calculating with Scheme.''
University of Oregon, Eugene, Oregon. March 1994. 
\item ``Extensible Denotational Specifications.''
ATT Bell Laboratories, Murray Hill, New Jersey. December 1993.
\item ``PCF, Sequentiality and Full Abstraction.''
Carnegie Mellon University, Pittsburgh, Pennsylvania. November 1993. 
\item ``Calculating with Scheme.''
Cornell University, Ithaca, New York, November 1993. 
\item ``The Essence of Compiling with Continuations.''
Universit{\"a}t Karlsruhe, Germany. June 1993.
\item ``Expressing and Reasoning about State.''
Tutorial at: {\it Workshop on State in Programming Languages\/},
Copenhagen, Denmark. June 1993.
\item ``Reasoning about Programs in CPS and Compiling without Continuations.''
ECRC, M\"unchen. December, 1992.
\item ``SPCF: Its Model, Calculus, and Computational Power.''
Invited talk at: North American Jumelage, Cornell. October, 1992.
\item ``Reasoning with Programs in Continuation-passing Style.''
INRIA Rocquencort. June, 1992. 
\item ``Observable Sequentiality and Full Abstraction.''
Universit\"at des Saarlandes. June, 1992.
\item ``SPCF: Models and Logics.''
Invited talk at: REX Workshop on Semantics -- Foundations and
Applications, June, 1992.
\item ``Observable sequentiality and full abstraction,''
Invited talk at: Categorical Logic in Computer Science, Aarhus, DK,
March, 1992. 
\item ``Observable sequentiality and full abstraction,'' 
MIT, Boston, MA. February, 1992.
\item ``Observable sequentiality and full abstraction.''
18th Annual Conference on the Principles of Programming Languages,
January, 1992.
\item ``Observable sequentiality and full abstraction,'' The
University of Texas at Austin. August, 1991.
\item ``On the Expressive Power of Programming Languages,''
\'Ecole Normale Superieure, Paris, France.May, 1991.
\item ``Reduction Semantics,'' \'Ecole Normale Superieure, Paris,
France. May, 1991. 
\item ``Extensible Operational Semantics,'' \'Ecole Polytechnique,
Paris, France. May 1991. 
\item ``Calculi and Models of Continuations,''
Oregon Graduate Institute, Portland, Oregon. February, 1991.
\item ``On the Expressive Power of Programming Languages,''
Oregon Graduate Institute, Portland, Oregon. February, 1991.
\item ``On the Expressive Power of Programming Languages,''
University of Iowa, Iowa City, Iowa. October, 1990. 
\item ``On the Expressive Power of Programming Languages,''
Universit\"at des Saarlands, Saarb\"ucken, FRG. July, 1990.
\item ``On the Expressive Power of Programming Languages,''
Stanford University, Stanford, CA, January (1990); 
\item ``On the Expressive Power of Programming Languages,''
ESOP'90. DIKU, Copenhagen, DK, May (1990). 
\item ``On the Expressive Power of Programming Languages,''
Carnegie Mellon University, Pittsburgh, Pennsylvania, April (1989)
\item ``On the Expressive Power of Programming Languages,''
University of Pennsylvania, Philadelphia, Pennsylvania, April (1989).
\item ``$\lambda$-v-CS: An extended $\lambda$-calculus for Scheme,''
1988 Conference on Lisp and Functional Programming, Snowbird, Utah,
July (1988).
\item ``Abstract continuations: A mathematical semantics for handling
full functional jumps,'' IBM Yorktown Heights, New York, June (1988).
\item ``The Theory and Practice of First-Class Prompts,'' Symposium
on Principles of Programming Languages, San Diego, January (1988).
\item ``Programming Languages and Calculi,'' The University of Austin,
Texas, October (1987).
\end{enumerate}
\end{document}
